Active Learning with Sentence Error Classification in Machine Translation

### 2020-10-10 Paper/error-classification.tex

In the most recent approaches, error detection and classification are examined as applications of neural sequence labeling methods, which aim to detect errors and predict their surrounding context \cite{rei2017semi}. The state of the art methods utilize powerful contextual word embeddings in an unsupervised setting \cite{bell2019context}, and overcome the disadvantages of prior methods that require large amounts of labeled data to perform efficiently.

>>>>

In most recent approaches, error detection and classification are examined as applications of neural sequence labeling methods, which aim to detect errors and predict their surrounding context \cite{rei2017semi}. The state of the art methods utilize powerful contextual word embeddings in an unsupervised setting \cite{bell2019context}, and overcome the disadvantages of prior methods that require large amounts of labeled data to perform efficiently.
